---
title: "Eriks Death counter"
format: pdf
editor: visual
---

Margit - 50 deaths
Radahn - 50+ deaths?
Morgott - 17 deaths
Godfrey - 13 deaths
-------- Etter mimic
Commander Niall - 2 deaths
Borealis the Freezing Fog (drage I mountaintops freezing) - 7 deaths
Fire Giant - 1 deaths
Godskin Duo - 1 deaths
Crucible knight random mob - 8 deaths
Placidusax -  0, mimic carry mens han drakk sæd
Enemy uten mimic -  4 deaths
Maliketh  - 2 deaths
Loretta - 1 death
Malenia - 39 deaths før han brukte mimic og drakk sæd

Total deaths: 155

```{r}
#Loading packages needed
library(tidyverse)

# Storing data in a tibble
deaths <- tibble(
  name = c("Margit", "Radahn", "Morgott", "Godfrey", "Commander Niall", "Borealis", "Fire Giant", "Godskin Duo", "Crucible knight", "Placidusax", "Enemy uten mimic", "Maliketh", "Loretta", "Malenia"),
  deaths = c(50, 50, 17, 13, 2, 7, 1, 1, 8, 0, 4, 2, 1, 39)
)

# Summing the total deaths
total_deaths <- deaths %>%
  summarise(deaths = sum(deaths)) %>%
# adding total deaths to the tibble and naming it total deaths
  mutate(name = "Total deaths") %>%
  select(name, deaths) %>%
  bind_rows(deaths, .)
```

```{r}
# Creating a bar plot
ggplot(total_deaths, aes(x = name, y = deaths)) +
  geom_col(fill = "cornflowerblue", alpha = 0.8) +
  geom_text(aes(label = deaths), vjust = -0.3, size = 3) +
  labs(title = "Eriks Death counter",
       x = "Bosses",
       y = "Deaths") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  # making the bars go from lowest to highest
  scale_x_discrete(limits = total_deaths$name[order(total_deaths$deaths)])
```

